\boldmath Supersymmetric Dirac-Born-Infeld Axionic Inflation and Non-Gaussianity

### 2018-09-17 SUSY_DBI_referee_reply.tex

5) The scan shown in Figure 1 contains no real information, unless one
specifies what is varied among the different points. The only information I
could find on this regard is Òwe allow $\alpha_1$ to varyÓ at the end of page 12.
How is it varied ? (in which range ? Is it a uniform sampling in linear units
? In log units ?) What is chosen for the other parameters of the model
? (?,?,A,T). How is the correct normalization of the scalar perturbations
enforced? (this is typically done by fixing the overall scale of the scalar
potential). Are subleading terms in $\frac{1}{T}$  important ? The scan strategy should T
be completely described, so that any reader, if interested, could precisely reproduce those figures.\\

\noindent {\it Reply
}}

6) The paper motivates the model from the trans-Planckian problem of axion inflation (the fact that we must take the axion scale 
$f > M_p$ in the original potential of natural inflation). It would be very interesting to provide also a scan of the values of f obtained for the various realizations presented in figures 1 and 2. Does this scan extend in the sub-Planckian region ? (the scan should be easily done, once the above questions 2.4 and 5 are answered).\\

\noindent {\it Reply\\
\pn{We agree with the suggestion of the referee. We have added a new figure 3 where we have presented 
 a scatter plot of $f_{eff}$ vs $f$ for the data sets of figures 1 and 2.
  }

### 2018-09-17 SUSY_DBI.tex
Delete .tex and Max: comments

 %\cite{Ade:2015ava}

@@

\begin{document} 
\maketitle
\flushbottom
%\fbox{{\today}}

@@

%  \begin{align}
%  f\equiv f_1=f_2= -\frac{2\mu}{\lambda}  - \sum_k \sum_{k=1}^m \frac{1}{2^{k/2-1}} k A_{k}  (\frac{-2\mu}{\lambda})^{k-1}
%  /\left[1+\frac{3}{2}(\frac{-2\mu}{\lambda}\right]  +\cdots
%  \end{align}

@@

  Non-Gaussianity is defined by the three-point correlation function of perturbations involving
  three scalars, two scalars and a graviton, two gravitons and a scalar and three gravitons~\cite{Maldacena:2002vr}.
  Since the work of~\cite{Maldacena:2002vr}  there has been
  a significant number of further analyses (see, e.g., \cite{Acquaviva:2002ud,Creminelli:2003iq,
  Silverstein:2003hf,Gruzinov:2004jx,Alishahiha:2004eh,Chen:2005fe,Creminelli:2005hu,
  Seery:2005wm,Babich:2004gb,Lyth:2005fi,Chen:2006nt, Huang:2007hh,Langlois:2008wt}).
  The dominant non-Gaussianity
  arises from the correlation function of three scalar perturbations. Thus for scalar perturbation $\zeta(\vec k)$ non-Gaussianity
  is defined by
  \begin{align}
    \left< \zeta(\vec k_1) \zeta(\vec k_2) \zeta(\vec k_3) \right> = (2\pi)^7 \delta^3(\vec k_1+ \vec k_2+ \vec k_3) \frac{\sum_i k_i^3}{\prod_i k_i^3}
    \left[ -\frac{3}{10} f_{NL} (P_k^{\zeta})^2 \right],
  \end{align}
  where $P_k^{\zeta}$ is the scalar power spectrum and $\pn{f_{NL}}$ is a measure of non-Gaussianity. 
  \pn{Non-Gaussianity depends strongly on  shape and various types of shapes have been discussed in the 
literature which include local, equilibrium and orthogonal ~\cite{Ade:2015ava} (For earlier analyses see 
\cite{Komatsu:2001rj,Komatsu:2003fd,Verde:1999ij}).
 The non-Gaussianity  we will discuss here is the one which has the shape of an equilateral triangle, 
 % of Eq. (\ref{equil}) is referred to in the
%literature as the equilibrium one which is indicated at the superscript ``equil''.}
  when $k_1=k_2=k_3$ and  is given by~\cite{Chen:2006nt}}
  \begin{align}
   \pn{f^{equil}_{NL}}= \frac{35}{108}\left(\frac{1}{c_s^2}-1\right) - \frac{5}{81} \left[ \left(\frac{1}{c_s^2} -1- 2\frac{z_2}{z_1}\right) + (3-2 {c}_1)z \frac{z_2}{z_1}\right] + {\cal O}(\epsilon).
    \label{equil}
  \end{align}
  where
  \begin{align}
    z_1= \beta L_{,\beta} + 2 \beta^2 L_{\beta\beta}\,,~~
    z_2= \beta^2 L_{,\beta \beta} + \frac{2}{3} \beta^3 L_{,\beta\beta\beta}\,,~~
    z= \frac{\dot z_2}{z_2 H}\,.
  \end{align}
 \pn{where the superscript ``equal''  on $f_{NL}$ indicates that we are specifically considering the shape to be of an equilateral 
 triangle. }

%\pn{
%Non-Gaussianity depends strongly on the shape and various types of shapes have been discussed in the 
%literature which include local, equilibrium and orthogonal ~\cite{Ade:2015ava} (For earlier analyses see 
%\cite{Komatsu:2001rj,Komatsu:2003fd,Verde:1999ij}).
% The non-Gaussianity of Eq. (\ref{equil}) is referred to in the
%literature as the equilibrium one which is indicated at the superscript ``equil''.}

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig1.pdf}
    \caption{
      Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the scalar spectral index $n_s$ 
      for the two field DBI model when $\alpha_1$ is allowed to vary, when $\alpha_2 = \alpha_3 = 0$. 
      The blue region enclosed by the blue line is the one allowed by experiment in the 2? range.      
            All the scatter points have pivot number of e-foldings in the range [50, 60].          
         $89\%$ of the simulated points 
      are consistent with Planck constraints as shown by green points while the red points lie outside the 68\% CL contour.
            Right panel: A plot of non-Gaussianity parameter $\pn{f^{equil}_{NL}}$ as
      a function of $\alpha_1$ for the same data set as in the left plot.  As in the left panel
      the green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region  
      and the red dots are parameter points which are outside the experimentally allowed region  on $r$ and $n_s$. 
      %The horizontal black line is the
 %lower limit $\pn{f^{equil}_{NL}} =5$ of the 
    %    projected value for observation in future experiments for non-Gaussianity.
    %       The points that lie above the black line give non-Gaussianity $f_\text{NL} > 5$ which, however, are not consistent with Eq.~(\ref{data}).
  \pn{Max: We need to remove the horizontal black line.}  
    }
    \label{fig1}
  \end{figure}

@@

  \pn{The most recent analyses of non-Gaussianity based on Planck data are given in ~\cite{Ade:2015ava}. 
  Here the analysis is done using cosmic microwave background (CMB) temperature and E-mode polarization 
  data. The  analysis using 
  temperature alone give $f^{equil} = -16 \pm 70$ (68 \% CL, statistical) and an analysis combining temperature and polarization data 
  gives $f^{equil} = -4 \pm 43$ (68 \% CL, statistical).}  
%  The analysis of~\cite{Komatsu:2001rj,Komatsu:2003fd,Verde:1999ij}
%  indicates that non-Gaussianity can be tested in data in future experiments provided $|\pn{f^{equil}_{NL}}|> 5$ and the $\pn{f^{equil}_{NL}}$
%  given by the right panel of Fig. (\ref{fig1}) lies significantly below that. In the analysis we allow a corridor of $[50,60]$
%  e-foldings and it is of interest to ask the dependence of $n_s$ and $\pn{f^{equil}_{NL}}$ on this number.
    In the left panel of Fig. (\ref{fig2})
  a plot of $n_s$ vs $N_{\rm pivot}$ is given. Here one finds that $n_s$ has a mild positive slope as a function of $N_{\rm pivot}$.
  The right panel gives a plot of $\pn{f^{equil}_{NL}}$ on $N_{\rm pivot}$. Here one finds the $\pn{f^{equil}_{NL}}$ has a relatively small variation in the range $[50,60]$ for
  $N_{\rm pivot}$. In either case one cannot draw any significant conclusion regarding the dependence of these parameters
  on the number of e-foldings as long as one is in the $N_{\rm pivot}$ range of $[50,60]$.

>>>>

@@

\begin{document} 
\maketitle
\flushbottom

@@

@@

  Non-Gaussianity is defined by the three-point correlation function of perturbations involving
  three scalars, two scalars and a graviton, two gravitons and a scalar and three gravitons~\cite{Maldacena:2002vr}.
  Since the work of~\cite{Maldacena:2002vr}  there has been
  a significant number of further analyses (see, e.g., \cite{Acquaviva:2002ud,Creminelli:2003iq,
  Silverstein:2003hf,Gruzinov:2004jx,Alishahiha:2004eh,Chen:2005fe,Creminelli:2005hu,
  Seery:2005wm,Babich:2004gb,Lyth:2005fi,Chen:2006nt, Huang:2007hh,Langlois:2008wt}).
  The dominant non-Gaussianity
  arises from the correlation function of three scalar perturbations. Thus for scalar perturbation $\zeta(\vec k)$ non-Gaussianity
  is defined by
  \begin{align}
    \left< \zeta(\vec k_1) \zeta(\vec k_2) \zeta(\vec k_3) \right> = (2\pi)^7 \delta^3(\vec k_1+ \vec k_2+ \vec k_3) \frac{\sum_i k_i^3}{\prod_i k_i^3}
    \left[ -\frac{3}{10} f_{NL} (P_k^{\zeta})^2 \right],
  \end{align}
  where $P_k^{\zeta}$ is the scalar power spectrum and $\pn{f_{NL}}$ is a measure of non-Gaussianity. 
  \pn{Non-Gaussianity depends strongly on  shape and various types of shapes have been discussed in the 
literature which include local, equilibrium and orthogonal ~\cite{Ade:2015ava} (For earlier analyses see 
\cite{Komatsu:2001rj,Komatsu:2003fd,Verde:1999ij}).
 The non-Gaussianity  we will discuss here is the one which has the shape of an equilateral triangle, 
  when $k_1=k_2=k_3$ and  is given by~\cite{Chen:2006nt}}
  \begin{align}
   \pn{f^{equil}_{NL}}= \frac{35}{108}\left(\frac{1}{c_s^2}-1\right) - \frac{5}{81} \left[ \left(\frac{1}{c_s^2} -1- 2\frac{z_2}{z_1}\right) + (3-2 {c}_1)z \frac{z_2}{z_1}\right] + {\cal O}(\epsilon).
    \label{equil}
  \end{align}
  where
  \begin{align}
    z_1= \beta L_{,\beta} + 2 \beta^2 L_{\beta\beta}\,,~~
    z_2= \beta^2 L_{,\beta \beta} + \frac{2}{3} \beta^3 L_{,\beta\beta\beta}\,,~~
    z= \frac{\dot z_2}{z_2 H}\,.
  \end{align}
 \pn{where the superscript ``equal''  on $f_{NL}$ indicates that we are specifically considering the shape to be of an equilateral 
 triangle. }

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{figs/fig1.pdf}
    \caption{
      Left panel: A plot of the ratio $r$ of the tensor to scalar power spectrum vs the scalar spectral index $n_s$ 
      for the two field DBI model when $\alpha_1$ is allowed to vary, when $\alpha_2 = \alpha_3 = 0$. 
      The blue region enclosed by the blue line is the one allowed by experiment in the 2? range.      
            All the scatter points have pivot number of e-foldings in the range [50, 60].          
         $89\%$ of the simulated points 
      are consistent with Planck constraints as shown by green points while the red points lie outside the 68\% CL contour.
            Right panel: A plot of non-Gaussianity parameter $\pn{f^{equil}_{NL}}$ as
      a function of $\alpha_1$ for the same data set as in the left plot.  As in the left panel
      the green dots are parameter points which satisfy the Planck constraints
      on $r$ and $n_s$ and lie in the blue region  
      and the red dots are parameter points which are outside the experimentally allowed region  on $r$ and $n_s$. 
    }
    \label{fig1}
  \end{figure}

@@

  \pn{The most recent analyses of non-Gaussianity based on Planck data are given in ~\cite{Ade:2015ava}. 
  Here the analysis is done using cosmic microwave background (CMB) temperature and E-mode polarization 
  data. The  analysis using 
  temperature alone give $f^{equil} = -16 \pm 70$ (68 \% CL, statistical) and an analysis combining temperature and polarization data 
  gives $f^{equil} = -4 \pm 43$ (68 \% CL, statistical).}  
    In the left panel of Fig. (\ref{fig2})
  a plot of $n_s$ vs $N_{\rm pivot}$ is given. Here one finds that $n_s$ has a mild positive slope as a function of $N_{\rm pivot}$.
  The right panel gives a plot of $\pn{f^{equil}_{NL}}$ on $N_{\rm pivot}$. Here one finds the $\pn{f^{equil}_{NL}}$ has a relatively small variation in the range $[50,60]$ for
  $N_{\rm pivot}$. In either case one cannot draw any significant conclusion regarding the dependence of these parameters
  on the number of e-foldings as long as one is in the $N_{\rm pivot}$ range of $[50,60]$.
